Probabilistic Catalogs for Crowded Stellar Fields

### 2013-03-10 paper/ms.tex
Wording

\section{Introduction}
Traditional practice in astronomy is to take images of the sky, detect
or enumerate sources visible in those images, and create catalogs.
These catalogs are then used to perform the fundamental astronomical
measurements, which might include something like the three-dimensional
structure of the Galaxy or the two-point correlation function of
galaxies.  Indeed, the process of catalog construction is so ``baked
in'' to our ideas about what astronomy is, we sometimes forget that
the catalog is \emph{not} the fundamental data product of astronomy; catalogs are produced
from imaging; their production involves many decisions and ideas
that go beyond the information provided to the telescope by the
incident intensity field. In addition, catalogs are not usually the final
goal of any imaging project or survey. Typically, they are produced in
order to facilitate the scientific study of populations of objects (e.g. the
initial mass function of a population of stars), or to provide a sky-search
capability to the community who might be interested in only a small subset of
objects. Standard tools for generating catalogs from astronomical imaging
include \sex~\citep{sextractor}, DAOPHOT \citep{1987PASP...99..191S}, 
DOLPHOT \citep{dolphot}, and SDSS
Photo \citep{photo}.

>>>>

\section{Introduction}
Traditional practice in astronomy is to take images of the sky, detect
or enumerate sources visible in those images, and create catalogs.
These catalogs are then used to perform fundamental astronomical
measurements, for example reconstructing the three-dimensional
structure of the Galaxy or the two-point correlation function of
galaxies.  Indeed, the process of catalog construction is so ``baked
in'' to our ideas about what astronomy is, we sometimes forget that
the catalog is \emph{not} the fundamental data product of astronomy; catalogs are produced
from imaging; their production involves many decisions and ideas
that go beyond the information provided to the telescope by the
incident intensity field. In addition, catalogs are not usually the final
goal of any imaging project or survey. Typically, they are produced in
order to facilitate the scientific study of populations of objects (e.g. the
initial mass function of a population of stars), or to provide a sky-search
capability to the community who might be interested in only a small subset of
objects. Standard tools for generating catalogs from astronomical imaging
include \sex~\citep{sextractor}, DAOPHOT \citep{1987PASP...99..191S}, 
DOLPHOT \citep{dolphot}, and SDSS
Photo \citep{photo}.
